### 2015-05-14 intro.tex
fixes

A major cause of concurrency bugs is the complicated and hostile environment in which drivers operate~\cite{corbet2005linux}. The Linux kernel can invoke drivers from multiple threads, a hardware device can issue interrupt requests that cause running processes to block and switch execution context, and the user may decide to remove a device (hot-plugging) while some operation is still running. All these scenarios can easily cause \emph{data races} if no proper synchronization mechanisms (e.g.\ locks) are in place to control concurrent access to shared resources.
%
Data races are a source of undefined behavior in C, and lead to nondeterministically occurring bugs that can be hard to reproduce, isolate and fix, especially in the context of complex operating systems.
%
Several techniques have been successfully used to analyze device drivers~\cite{ball2006thorough, clarke2004predicate, engler2000checking, henzinger2002temporal, cook2006termination, kuznetsov2010testing, renzelmann2012symdrive, lal2012corral}, but most focus on generic sequential program properties and protocol bugs. Linux kernel analyzers, such as sparse~\cite{corbet2004sparse}, coccinelle~\cite{padioleau2008doc} and lockdep~\cite{corbet2006lock}, can find deadlocks in kernel source code, but are unable to detect races. Techniques that can detect races in drivers~\cite{qadeer2004kiss, pratikakis2006locksmith, voung2007relay, lal2012corral} are usually either \emph{unsound} (i.e.\ can miss real bugs) or \emph{imprecise} (i.e.\ can report false bugs), and typically sacrifice precision for scalability. Thus, there is a clear need for new tools that are able to detect races efficiently and precisely.

>>>>

A major cause of concurrency bugs is the complicated and hostile environment in which drivers operate~\cite{corbet2005linux}. The Linux kernel can invoke drivers from multiple threads, a hardware device can issue interrupt requests that cause running processes to block and switch execution context, or the user may decide to remove a device (hot-plugging) while some operation is still running. All these scenarios can easily cause \emph{data races} if no proper synchronization mechanisms (e.g.\ locks) are in place to control concurrent access to shared resources.
%
Data races are a source of undefined behavior in C, and lead to nondeterministically occurring bugs that can be hard to reproduce, isolate and fix, especially in the context of complex operating systems.
%
Several techniques have been successfully used to analyze device drivers~\cite{ball2006thorough, clarke2004predicate, engler2000checking, henzinger2002temporal, cook2006termination, kuznetsov2010testing, renzelmann2012symdrive, lal2012corral}, but most focus on generic sequential program properties and protocol bugs. Linux kernel analyzers, such as sparse~\cite{corbet2004sparse}, coccinelle~\cite{padioleau2008doc} and lockdep~\cite{corbet2006lock}, can find deadlocks in kernel source code, but are unable to detect races. Techniques that can detect races in drivers~\cite{qadeer2004kiss, pratikakis2006locksmith, voung2007relay, lal2012corral} are usually either \emph{unsound} (i.e.\ can miss real bugs) or \emph{imprecise} (i.e.\ can report false bugs), and typically sacrifice precision for scalability. Thus, there is a clear need for new tools that are able to detect races efficiently and precisely.
